### 2017-03-06 vargo/loopStates.Rmd
Increased upper limits of walk and cycle vectors to 60 (from 20)

Foo.
```{r libs, eval = TRUE, echo = TRUE, results = "show", warning = TRUE, error = TRUE, message = TRUE}
library(devtools)
install_github("syounkin/ITHIM", ref="devel", force=TRUE)
library("ITHIM")
library("tidyr")
packageVersion("ITHIM")
rm(list=ls())

######## read in ITHIM objects #######
#available at https://uwmadison.box.com/shared/static/06doqkc3aiaoqdb569r7si1vthlyvgu9.rds
#states <- readRDS("~/Downloads/ITHIMList.by.state.rds")
states <- readRDS("~/GHI/R/data/ITHIMList.by.state.rds")

@@

n <- 5
ntVec <- c(2, 5, 10) # must be ordered and have length 3

@@

    base <- states[[state]]
    base <- update(base, list(quantiles = seq(0.1,0.9,by=0.1)))

@@

    wVec <- baseWalk + seq(0, 20, length.out = n)
    cVec <- baseCycle + seq(0, 20, length.out = n)

@@

## allStatesResults <- within(allStatesResults,{
##                            pctTotalDALYS = deltaDALY.all/DALY.all
##                            pctBreastCancer = deltaDALY.BreastCancer/DALY.BreastCancer
##                            pctColonCancer = deltaDALY.ColonCancer/DALY.ColonCancer
##                            pctCVD = deltaDALY.CVD/DALY.CVD
##                            pctDementia = deltaDALY.Dementia/DALY.Dementia
##                            pctDepression = deltaDALY.Depression/DALY.Depression
##                            pctDiabetes = deltaDALY.Diabetes/DALY.Diabetes
## })

>>>>

Foo.
```{r states, eval = TRUE, echo = TRUE, results = "show", warning = TRUE, error = TRUE, message = TRUE}

library(devtools)
install_github("syounkin/ITHIM", ref="devel", force=TRUE)
library("ITHIM")
library("tidyr")
packageVersion("ITHIM")
rm(list=ls())

states <- readRDS("~/GHI/R/data/ITHIMList.by.state.rds")

@@

n <- 5 # length of walk and cycle vectors
ntVec <- c(2, 5, 10) # must be ordered and have length 3

@@

    base <- states[[state]]
    base <- update(base, list(quantiles = seq(0.1, 0.9, by = 0.1)))

@@

    wVec <- baseWalk + seq(0, 60, length.out = n)
    cVec <- baseCycle + seq(0, 60, length.out = n)

@@
